### 2017-02-06 R/cambridge.Rmd
Update to cambridge.Rmd

ITHIM.baseline.sim <- update(ITHIM.baseline, list(roadInjuries = simRI))
    ITHIM.scenario.sim <- updateRoadInjuries(ITHIM.baseline.sim, ITHIM.scenario)
    RIburden <- computeRoadInjuryBurden(ITHIM.baseline.sim, ITHIM.scenario.sim)
    deltaDeaths <- sum(subset(RIburden, burden == "dproj")$delta)
cat(c(deltaDeaths, "\n"))
```

>>>>

ITHIM.baseline.sim <- update(ITHIM.baseline, list(roadInjuries = simRI))
ITHIM.scenario.sim <- updateRoadInjuries(ITHIM.baseline.sim, ITHIM.scenario)
RIburden <- computeRoadInjuryBurden(ITHIM.baseline.sim, ITHIM.scenario.sim)
deltaDeaths <- sum(subset(RIburden, burden == "dproj")$delta)

```
